{\ttlit Bug Seeding}, On the importance of Previous Commit

### 2016-01-20 paperMSR.tex
Modifying the abstract

\maketitle
\begin{abstract}
\textbf{Algorithms such as SZZ have been proposed to identify the cause of a \textit{fixed} bug, some of these algorithms rely on the fact that bugs in source code have been originated in the previous commit, understanding previous commit as the fix-inducing commit. However, there has been no enough empirical evidences to prove this assumption, and taking into account that exist projects with different nature, ones more active that others, might happen that this assumption is not fulfilled in projects with present this characteristic.}

>>>>

\maketitle
\begin{abstract}
\textbf{Algorithms such as SZZ have been proposed to identify the cause of a \textit{fixed} bug, some of these algorithms rely on the fact that bugs in source code have been originated in the previous commit, understanding previous commit as the fix-inducing commit. However, there has been no enough empirical evidences to prove this assumption, and taking into account that exist projects with different nature, ones more active that others, might happen that this assumption is not fulfilled in projects which present this characteristic.}
